### 2014-07-18 R/Test_Neutral_simul.Rmd
Several modifications to Rmd

# Multifractal analysis of multispecies spatial distributions - Model simulations

@@

```{r generateLogSerParms}

s_wait <- F # variable to make R wait until simulations ends or not

@@

# Generate a SAD for metacommunity using a logseries 
#
# side is the side of the simulation lattice
#
# N is the total number of individuals 
#
# S is the species richness 
#

@@

system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

@@

Now I will read the output generated from simulations (not from pomac) to test if the SAD are equal in time using Kolmogorov Smirnov test.

```{r testRAD_KS}

@@

Let try simulations with different parameters using pomac and at Time=100

```{r simul_pomac467}

setwd("Simul")

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100
# Change interval to measure Density and Diversity
par[par$V1=="inter",]$V2 <- 100
par[par$V1=="init",]$V2 <- 100

par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

# delete old simulations
system("rm Exp467*")

system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

Now I will read the densities for different parameters and test SADs and Shannon

```{r testKS_pomac467}

den1 <- meltDensityOut_NT("Simul/Exp467Density.txt",nrow(ff))

parms <- unique(den1[,1:4])
combo <- combn(nrow(parms),2)

require(plyr)
mks <-adply(combo,2, function(x) {
      p1 <- parms[x[1],]
      p2 <- parms[x[2],]
      d1 <- merge(den1,p1)
      d2 <- merge(den1,p2)
      ks <- ks.test(d1$value,d2$value)
      out <-data.frame(p1,p2,t(paste(p1,p2,sep="_")),p.value=ks$p.value,stringsAsFactors=F)
      ln <-length(names(p1))*3
      names(out)[1:ln]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2),names(p1))
      return(out)      
      })

#p1 <- parms[1,]
#p2 <- parms[9,]
#d1 <- merge(den1,p1)
#d2 <- merge(den1,p2)
#ks <- ks.test(d1$value,d2$value)
#out <-data.frame(p1,p2,t(paste(p1,p2,sep="_")),p.value=ks$p.value,stringsAsFactors=F)
#ln <-length(names(p1))*3
#names(out)[1:ln]<-c(paste0(abbreviate(names(p1)),1),paste0(abbreviate(names(p1)),2),names(p1))
#rm(d1,d2,p1,p2,out,ks,ln)

mks$p.adjust <- p.adjust(mks$p.value, method="hommel")

# wich are not different

format(mks[mks$p.adjust>0.05,c(10:13,14:15)],digits=4)
format(mks[mks$p.adjust>0.1,c(10:13,14:15)],digits=4)

format(mks[mks$p.value>0.01,c(10:13,14:15)],digits=4)

# SE PODRIA HACER CON ddply para hacer varias filas del mks !!!!!

#den2 <- ddply(den1,.(Time), function(x) { 
  #tmp <- x[x$value>0,]
#  tmp <- x[order(x$value),]
#  tmp$Ord <- nrow(x):1
#  data.frame(tmp)
#  })

format(mks[mks$p.value<0.05 & mks$p.adjust>0.05,c(10:13,14:15)],digits=4)

psa <-mergePairSAD(mks[61,],den1)
# p.value = 
require(ggplot2)
g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line()
g

psa <- mergePairSAD(mks[105,],den1)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())
g + geom_point()
```

In this case there are no semejant SAD for different mechanisms (neutral vs hierarchical) but some of adjusted p values lead to not reject differences when SADs seems different like mks[61,],105,107

Now I will simulate with a smaller Replacement = 0.01 / 0.1 and compare with Replacement=0

```{r simul_pomac467_R001,echo=F,message=F,warning=F}

setwd("Simul")

# read par file with simulations parameters

par <- read.table("sim.par",quote="",stringsAsFactors=F)

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100

par[par$V1=="inter",]$V2 <- 100 # interval to measure Density and Diversity
par[par$V1=="init",]$V2 <- 100  # Firs time of measurement = interval
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters

# I will not delete old simulations
# system("rm Exp467*")

# I have to modify pomExp.lin to make different simulations
#undebug(genPomacParms)

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0.01))

system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

# add more paremeter combinations 
genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0.1,0.01))
system("cp pomExp.lin pomac.lin")
system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

# Read all simulations and change to long format

den1 <- meltDensityOut_NT("Simul/Exp467Density.txt",nrow(ff))

pairKS_SAD(den1)

format(mks[mks$p.adjust>0.05,c(10:13,14:15)],digits=4)

nrow(mks[mks$p.adjust>0.05,c(10:13,14:15)])/nrow(mks)

psa <- mergePairSAD(mks[468,],den1)

require(ggplot2)

(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

The proportion of equal distributions is 0.30 what happens if we test Dq

>>>>

# TEST for Multifractal analysis of multispecies spatial distributions - Model simulations

@@

```{r setup, eval=T }

s_wait <- T # variable to make R wait until simulations ends or not

simul  <- F # variable to perform or not the simulations

@@

# Set the location of the binary 
#
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"

## Generate a metacommunity using a logseries

side: is the side of the simulation lattice

N: is the total number of individuals

S: is the species richness

```{r generateLogSerParms, eval=FALSE,echo=F,message=F,warning=F}
# Generate a SAD for metacommunity using a logseries 
#
# side is the side of the simulation lattice
#
# N is the total number of individuals 
#
# S is the species richness 
#

@@

# make simulations
if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

@@

## Test: Simulations with Time 1-100

Now I will read the output generated from simulations (not from pomac) to test if the SAD are equal in time using Kolmogorov Smirnov test. These simulations have TIME as a variable

```{r testRAD_KS,eval=FALSE, echo=F,message=F,warning=F}

@@
